Composing Robustly Safe Compilers

### 2023-06-09 popl/main.tex
Add overview

\BrText{Overview}{This paper introduces a formal framework for secure compiler compositions and showcases the framework's power by instantiating it on a multi-level compilation chain.
To this end, we discuss security property compositions and define several secure compilers, where each is either robustly preserving a different security property of interest or optimizing, i.e., applying \gls{cf} or doing \gls{dce}.
We compose these secure compilers into a multi-level compilation chain which is optimizing and robustly preserves a combination of \gls{ms} and \gls{cct}.
Crucially, the robust preservation proofs are only done for the individual compilers in the compilation chain and the robust preservation for the whole chain is a result of one of our key theorems.
The key results are formalized in Coq.}

In summary, this paper makes the following contributions:

@@

  \item Our key contributions are formalized in the Coq proof assistant.
        The formalization for the compilers are \emph{extractable}.
        That is, one can translate our Coq code to Ocaml and run them.
        Finally, in this paper, whenever definitions or proofs are done in Coq, we use the symbol \CoqSymbol.
\end{itemize}

@@

\section{Composing Properties}\label{sec:compprop}
\section{Composing Robustly Secure Compilers}\label{sec:compcomp}
This section presents three different kinds of secure compiler compositions and their corresponding proofs.

\section{Case Study: Memory Safe and Cryptographic Constant Time Code}\label{sec:casestud}
This section defines several secure compilers, each of which robustly preserves a different property of interest.
We demonstrate the power of our framework from \Cref{sec:compprop,sec:compcomp} by composing these compilers for a secure, but optimizing, compilation chain that robustly preserves \gls{ms} and \gls{cct}.
Concretely, \Cref{subsec:cs:tms} describes robust preservation of \gls{tms}. % by compiling from a language with a strong, static type system to a language without any type system.
\Cref{subsec:cs:ms} describes the robust preservation of \gls{sms} and, when composed with the compiler for \gls{tms}, \gls{ms}.
\Cref{subsec:cs:scct} composes the compiler for \gls{ms} with another one that robustly preserves \gls{cct}.
We attain our final compilation chain in \Cref{subsec:cs:opts}, which defines optimizing compilers performing either \gls{cf} or \gls{dce} and composes them with the ones from \Cref{subsec:cs:tms,subsec:cs:ms,subsec:cs:scct}.

>>>>

\BrText{Solution}{This paper introduces a formal framework for secure compiler compositions and showcases the framework's power by instantiating it on a multi-level compilation chain.
To this end, we discuss security property compositions and define several secure compilers, where each is either robustly preserving a different security property of interest or optimizing, i.e., applying \gls{cf} or doing \gls{dce}.
We compose these secure compilers into a multi-level compilation chain which is optimizing and robustly preserves a combination of \gls{ms} and \gls{cct}.
Crucially, the robust preservation proofs are only done for the individual compilers in the compilation chain and the robust preservation for the whole chain is a result of one of our key theorems.
The key results are formalized in Coq.}

\BrText{Validation}{In summary, this paper makes the following contributions:

@@

  \item Our key contributions are formalized in the Coq proof assistant.
        The formalization for the compilers are \emph{extractable}.
        That is, one can translate our Coq code to Ocaml and run them.
        Finally, in this paper, whenever definitions or proofs are done in Coq, we use the symbol \CoqSymbol.
\end{itemize}}

@@

\section{Composing Properties}\label{sec:compprop}
\section{Composing Robustly Secure Compilers}\label{sec:compcomp}
This section studies different kinds of secure compiler compositions and their corresponding proofs.
Most notably, it looks at the sequential composition of secure compilers and shows a theorem that allows for modular proof engineering: compilers need not to robustly preserve the same property in order to be securely composed.
Moreover, it demonstrates that the order does not matter for composing compilers with the same source and target language.

\section{Case Study: Memory Safe and Cryptographic Constant Time Code}\label{sec:casestud}
This section defines several secure compilers, each of which robustly preserves a different property of interest.
We demonstrate the power of our framework from \Cref{sec:compprop,sec:compcomp} by composing these compilers for a secure, but optimizing, compilation chain that robustly preserves \gls{ms} and \gls{cct}.
Concretely, \Cref{subsec:cs:tms} starts by defining languages $\src{L_{TMS}}$ and $\trg{L}$ and describes a compiler $\llbracket\src{\bullet}\rrbracket^{\src{L_{TMS}}\to\trg{L}}$ for the robust preservation of \gls{tms} between the two languages.
\Cref{subsec:cs:ms} defines $\irl{L_{MS}}$ and a compiler $\llbracket\trg{\bullet}\rrbracket^{\trg{L}\to\irl{L_{MS}}}$ that robustly preserves \gls{sms}.
By the framework presented in \Cref{sec:compcomp,sec:compprop}, we attain a compiler $\llbracket\src{\bullet}\rrbracket^{\src{L_{TMS}}\to\irl{L_{MS}}}$ for the robust preservation of \gls{ms} by composing $\llbracket\src{\bullet}\rrbracket^{\src{L_{TMS}}\to\trg{L}}$ and $\llbracket\trg{\bullet}\rrbracket^{\trg{L}\to\irl{L_{MS}}}$.
\Cref{subsec:cs:scct} defines $\obj{L_{CCT}}$ and a compiler $\llbracket\irl{\bullet}\rrbracket^{\irl{L_{MS}}\to\obj{L_{CCT}}}$ that robustly preserves \gls{cct}.
Composing it with $\llbracket\src{\bullet}\rrbracket^{\src{L_{TMS}}\to\irl{L_{MS}}}$ yields $\llbracket\src{\bullet}\rrbracket^{\src{L_{TMS}}\to\obj{L_{CCT}}}$, a compiler that robustly preserves a combination of \gls{ms} and \gls{cct}.
We attain our final compilation chain in \Cref{subsec:cs:opts}, which defines optimizing compilers performing either \gls{cf} or \gls{dce} and composes them with $\llbracket\src{\bullet}\rrbracket^{\src{L_{TMS}}\to\obj{L_{CCT}}}$, giving us an optimizing, secure compilation chain.
